Efficiently stable presentations from error-correcting codes

### 2025-10-16 efficient_stability.tex
Updates from Overleaf

>>>>

\begin{remark}
    Definition \ref{def:eff-stab} is often called in the literature ``flexible pointwise Hilbert--Schmidt stability (in the class $C$)''. There are other versions of stability, such as: $\bullet$ the non-flexible one (cf.\ \cite{becker2019stability, hadwin2018stability}), in which one does not allow to compare representations of different dimensions; $\bullet$ uniform stability, in which almost representations are with respect to  the (often) infinite multiplication table presentation (cf.\ \cite{kazhdan1982e,becker2022stability}); $\bullet$ stability in permutations, where instead of studying approximate representations one studies approximate actions (cf.\ \cite{becker2019stability,becker2020group, ioana2020stability}) and so on. In the cited papers above there are thorough literature surveys that we avoid herein. 
\end{remark}
